A paradigm for \earlywarning\ detection of compact binary coalescence in the context of multi-messenger astronomy

### 2011-06-29 method.tex
Moved sky localization discussion into its own section; merged subsections in introduction; juggled paragraphs discussing EM counterparts
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1210 ccdd05d5-56c1-461a-bf98-85f6876523b4
Deleted commented-out text
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1211 ccdd05d5-56c1-461a-bf98-85f6876523b4

\section{Early warning searches for compact binary coalescence}
\label{sec:method}

@@

\subsection{Conventional \CBC{} matched filter searches}

@@

\begin{comment}
An example time slice design satisfying these constraints for a $1.4 - 1.4 \,
M_{\odot}$ binary is shown in Table~\ref{table:time_slices}.
%
\begin{table}[h!]
\begin{minipage}[c]{0.52\textwidth}
\centering
\vspace{0.8cm}
\includegraphics{time_slices.pdf}
\end{minipage}
\begin{minipage}[c]{0.3\textwidth}
\centering
\input{time_slices.tex}
\end{minipage}
\caption{\label{table:time_slices} Example of nearly critically sampled,
power-of-two time slices for a $1.4 - 1.4 \, M_{\odot}$ template extending from
$f_\mathrm{low} = 10 \, \mathrm{Hz}$ to $f_\mathrm{hi} = f_\mathrm{ISCO} = 1571\, \mathrm{Hz}$
with a time-frequency structure given by ($\ref{eq:fgw})$. $f^s$ is the sample
rate of the time slice, $(t^{s+1}, t^s]$ are the boundaries in seconds
preceding coalescence and \slicessamps\ is the number of samples in the
$s^{\mathrm{th}}$ filter.}
\end{table}
\end{comment}

>>>>

\section{Novel data analysis strategy}
\label{sec:method}

@@

\subsection{Conventional \CBC{} searches}

@@
